---
title: "coevolution STERGM"
author: "Kirk Li"
date: "09/23/2014"
output:
  html_document:
    number_sections: yes
    toc: yes
---
# Coevolution STERGM
###############################################################################
```{r}
try(setwd("Rmd"))
opts_chunk$set(cache=TRUE)
op <- par()
par(mfrow=c(1,1),mar=c(3,3,1,1), mgp=c(2,1,0))
np <- par()

fls <-list.files("../../",recursive=T)
source(paste0("../../",fls[grep("kk_utils/utils.R",fls)]))
source(paste0("../../",fls[grep("cotergm/R/functions.R",fls)]))
fig.path = "figures/"
# .libPaths(cotergm)
library("statnet.common",lib=cotergm)
library("network",lib=cotergm)
library("ergm",lib=cotergm)
library("tergm",lib=cotergm)
set.seed(123)
```

```{r}
net1 <-as.network(read.table("../s50_data/s50-network1.dat"))
net2 <-as.network(read.table("../s50_data/s50-network2.dat"))
net3 <-as.network(read.table("../s50_data/s50-network3.dat"))
alcohol <- read.table("../s50_data/s50-alcohol.dat")
drugs <- read.table("../s50_data/s50-drugs.dat")
net <- net1

d2ud <- function(net){
	net <- as.matrix(net)
	for (i in 1:nrow(net)){
		for(j in 1:nrow(net)){
			net[i,j] = max(net[i,j],net[j,i])
		}}
	as.network(net,directed=FALSE)
}

net1 <- d2ud(net1)
net2 <- d2ud(net2)
net3 <- d2ud(net3)

al1 <- as.numeric(alcohol[,1]>3)+1
al2 <- as.numeric(alcohol[,2]>3)+1
net1 %v% "status" <- al1
net2 %v% "status" <- al2

y0 <- net1
nw <- net2
```




```{r}
# Formation Plus Network
FP <- FP.nw(y0,nw,"status")
# Formation Minus Network
FM <- FM.nw(y0,nw,"status")
# Dissolution Plus Network
DP <- DP.nw(y0,nw,"status")
# Dissolution Minus Network
DM <- DM.nw(y0,nw,"status")
```


```{r}
constraints=~atleastnonminus(y0)

MHproposal <- MHproposal(constraints,nw=y0,arguments=list())

summary(y0~edges+plus+nodematch_cotergm("status",diff=TRUE),MHproposal=MHproposal)
summary(nw~edges+plus+nodematch_cotergm("status",diff=TRUE),MHproposal=MHproposal)


summary(FP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=0),MHproposal=MHproposal)
summary(FP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=1),MHproposal=MHproposal)
summary(FP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=2),MHproposal=MHproposal)
summary(FM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=0),MHproposal=MHproposal)
summary(FM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=1),MHproposal=MHproposal)
summary(FM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=2),MHproposal=MHproposal)
summary(DP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=0),MHproposal=MHproposal)
summary(DP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=1),MHproposal=MHproposal)
summary(DP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=2),MHproposal=MHproposal)
summary(DM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=0),MHproposal=MHproposal)
summary(DM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=1),MHproposal=MHproposal)
summary(DM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=2),MHproposal=MHproposal)
```



























```{r, warning=FALSE}

fit1.edges <- ergm(FP~edges,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonminus(y0),verbose=0, eval.loglik=F)

fit1.plus <- ergm(FP~plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonminus(y0),verbose=0, eval.loglik=F)


fit1.edges_plus <- ergm(FP~edges+plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonminus(y0),verbose=0, eval.loglik=F)



fit1.edges_plus_nodematch <- ergm(FP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=2,keep=2),control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonminus(y0),verbose=0, eval.loglik=F)
```

```{r, warning=FALSE}




fit2.edges <- ergm(FM~edges,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonplus(y0),verbose=0, eval.loglik=F)

fit2.plus <- ergm(FM~plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonplus(y0),verbose=0, eval.loglik=F)


fit2.edges_plus <- ergm(FM~edges+plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonplus(y0),verbose=0, eval.loglik=F)


fit2.edges_plus_nodematch <- ergm(FM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0edge=2,keep=1),control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atleastnonplus(y0),verbose=0, eval.loglik=F)

```

```{r, warning=FALSE}



fit3.edges <- ergm(DP~edges,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonminus(y0),verbose=0, eval.loglik=F)

fit3.plus <- ergm(DP~plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonminus(y0),verbose=0, eval.loglik=F)


fit3.edges_plus <- ergm(DP~edges+plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonminus(y0),verbose=0, eval.loglik=F)


fit3.edges_plus_nodematch <- ergm(DP~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=2,keep=1),control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonminus(y0),verbose=0, eval.loglik=F)


```{r, warning=FALSE}




fit4.edges <- ergm(DM~edges,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonplus(y0),verbose=0, eval.loglik=F)

fit4.plus <- ergm(DM~plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonplus(y0),verbose=0, eval.loglik=F)


fit4.edges_plus <- ergm(DM~edges+plus,control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonplus(y0),verbose=0, eval.loglik=F)


fit4.edges_plus_nodematch <- ergm(DM~edges+plus+nodematch_cotergm("status",diff=TRUE,y0nodal=2,keep=2),control=control.ergm(MCMC.burnin=10000,MCMC.samplesize=10000,MCMC.interval=100,MCMLE.maxit=20,MCMLE.min.effectiveSize=20,MCMC.max.interval=100), constraints=~atmostnonplus(y0),verbose=0, eval.loglik=F)
```


```{r,warning=FALSE}
fit1.list <- lapply(ls()[grep("fit1",ls())][c(1,4,2,3)],function(x)eval(parse(text=paste0('summary(',x,')$coef'))))

fit2.list <- lapply(ls()[grep("fit2",ls())][c(1,4,2,3)],function(x)eval(parse(text=paste0('summary(',x,')$coef'))))

fit3.list <- lapply(ls()[grep("fit3",ls())][c(1,4,2,3)],function(x)eval(parse(text=paste0('summary(',x,')$coef'))))

fit4.list <- lapply(ls()[grep("fit4",ls())][c(1,4,2,3)],function(x)eval(parse(text=paste0('summary(',x,')$coef'))))

fit1.list
fit2.list
fit3.list
fit4.list
```


